Boosting

### 2021-12-07 boosting.Rmd
Fixed file name error
Henrique's Boosting

boost <- gbm(HeartDisease~.,data=temp_train,n.trees=1000,shrinkage=4,interaction.depth = 2 ,distribution = "bernoulli")

@@

@@

>>>>

oob = trainControl(method = "oob")
cv_5 = trainControl(method = "cv", number = 5)

@@

seat_gbm_tune = train(as.factor(HeartDisease) ~ ., data = train,
                      method = "gbm",
                      trControl = cv_5,
                      verbose = FALSE,
                      tuneGrid = gbm_grid)

plot(seat_gbm_tune)

@@

```{r}
boost <- gbm(HeartDisease~.,data=train,n.trees=1000,shrinkage=0.01,interaction.depth = 1 ,distribution = "bernoulli")

boostpred = ifelse(predict(boost,test, n.trees = 2000, "response") > 0.5, 
                             "1", "0")

confm2<-table(predicted = boostpred, actual = test$HeartDisease)
confm2
error<-(confm2[1,1]+confm2[2,2])/sum(confm2)
error
```
